### 2016-01-13 README.Rmd
Fixed some inaccuracies in README. Alphabetized author list by last name.
Added a brief 'More Information' snippet to direct users to our vignette to find any particulars.

# qmj (Quality Minus Junk)
Authors : Anthoney Tsou, Eugene Choe, David Kane, Ryan Kwon

@@

rawdata <- get_info(companies)

@@

rawprices <- get_prices(companies)

@@

>>>>

# qmj (Quality Minus Junk)
Authors : Eugene Choe, David Kane, Ryan Kwon, Anthoney Tsou

@@

rawdata <- get_info(custom_companies)

@@

rawprices <- get_prices(custom_companies)

@@

##More Information
More information, especially regarding methodology and what measures were used to filter out companies with bad or insufficient data, may be found in our vignette.
